Motion planning for assessing accessibility of protein tunnels

### 2017-09-10 paper.tex
alg

Instead, we propose to expand the tree by considering all conformations and also by expanding the tree using the maximal possible scale that
does not lead to a collision.
For each ligand conformation $l \in \L$, the expansion procedure attempts to find a new collision-free configuration around $\qnear$ with a maximal scale.
First, the maximal scale $\smax \in \S$ is selected and $m$ random samples are generated around $\qnear$ (in the distance $\varepsilon$) 
and tested for collisions.
The nearest collision-free sample towards $\qrand$ is selected and added to the tree.
If none of the tested samples is collision-free, the scale is reduced to $\smax-\sdelta$ and the search continues
until a collision-free sample is found or until the minimal reduced-scale $\smin$ is reached.
The random samples are generated similarly as in the case of $\qrand$ samples, only their translation
part $(x,y,z)$ is generated around $\qnear$.

@@

\subsection{Influence of conformation selection}

>>>>

The expansion procedure attempts to expand the tree using all the conformations $\L$ and by preferring larger scales than the smaller ones.
For each $l \in \L$, the expansion procedure attempts to find a new collision-free configuration around $\qnear$ with a maximal scale.
First, the maximal scale $\smax \in \S$ is selected and $m$ random samples are generated around $\qnear$ (in the distance $\varepsilon$) 
and tested for collisions.
The random samples are generated similarly as in the case of $\qrand$ samples, only their translation
part $(x,y,z)$ is generated around $\qnear$.
The nearest collision-free sample towards $\qrand$ is selected and added to the tree.
If none of the tested samples is collision-free, the scale is reduced to $\smax-\sdelta$ and the search continues
until a collision-free sample is found or until the minimal reduced-scale $\smin$ is reached.
By testing first the largest scale ($\smax$), the expansion procedure preffers expanding the tree by larger scales.
This forces the planner to automatically use smaller scaled in the difficult (narrow) parts of the tunnels, while prefering
large scales if possible.

@@

\subsection{Influence of the conformation selection}
